\documentclass[12pt,a4paper,oneside]{article}

\usepackage[margin=3cm]{geometry}

\usepackage{hyperref}
\hypersetup{
    pdftitle={COM 250, Mobile Application Development},%
    pdfauthor={Toksaitov Dmitrii Alexandrovich},%
    pdfsubject={Syllabus},%
    pdfkeywords={COM;}{250;}{syllabus;}{mobile;}{application;}{development},%
    colorlinks,%
    linkcolor=black,%
    citecolor=black,%
    filecolor=black,%
    urlcolor=black
}

\newcommand{\R}[1]{\uppercase\expandafter{\romannumeral #1\relax}}

\begin{document}

    \title{COM 250, Mobile Application Development}
    \author{
        American University of Central Asia\\
        Software Engineering Department
    }
    \date{}
    \maketitle

    \section{Course Information}

        \begin{description}
            \item[Course ID]\hfill\\
                COM 250, 3371, 3156
            \item[Course Repositories]\hfill\\
                \url{https://github.com/auca/com.250}
            \item[Place]\hfill\\
                AUCA, laboratory G30, G31
            \item[Time]\hfill\\
                Monday 9:25\\
                Friday 9:25
        \end{description}

    \section{Prerequisites}

        COM 112, Programming \R{2}

    \section{Contact Information}

        \begin{description}
            \item[Instructor]\hfill\\
                Toksaitov Dmitrii Alexandrovich\\
                \href{mailto:toksaitov_d@auca.kg}{toksaitov\_d@auca.kg}
            \item[Office]\hfill\\
                AUCA, room 315\\
                AUCA, Media Laboratory
            \item[Office Hours]\hfill\\
                Monday 12:45--17:00\\
                Tuesday 15:35--17:00\\
                Thursday 12:45--17:00\\
                Friday 12:45--17:00
        \end{description}

    \section{Course Overview}

        This course introduces students to development tools and APIs to build
        applications for the Google Android operating system. Students will
        learn how to build unique interactive user interfaces for multi-touch
        mobile devices. The course covers object-oriented design using the
        Model-View-Controller paradigm, the Java programming language for the
        Android Runtime, development frameworks, device emulators, and
        application build tools. Other topics include multi-threading, power and
        performance considerations, the accelerated 2-D and 3-D graphics APIs.

    \section{Topics Covered}

        \begin{itemize}
            \item Development tools (Android Studio, SDK, device emulators)
            \item App. fundamentals (activities, services, content providers)
            \item User interface elements
            \item Graphics and animation
            \item Data storage
            \item Connectivity
            \item Media and camera
            \item Working with device sensors
            \item Publishing and distributing applications
        \end{itemize}

    \section{Practice Tasks}

        Students are required to finish 10 practice tasks. The tasks are based
        on topics discussed during lectures. Each task should be finished during
        the class to receive a grade.

    \section{Course Projects}

        Each student will have to develop an app for the Android platform. The
        challenge of the project is to maintain a certain level of quality for
        the application to be able to publish it to end users on Google Play
        Store at the end of the course.

    \section{Final Exam}

        At the end of the course, students have to take the final examination in
        a form of a quiz with a number of multiple choice questions on topics
        discussed during classes.

    \section{Reading}

        \begin{enumerate}
            \item Introduction to Android Application Development: Android
            Essentials, 5th Edition by Joseph Annuzzi Jr., Lauren Darcey, Shane
            Conder (ISBN: 978-0134389455)
            \item Java: A Beginner's Guide, 6th Edition by Herbert Schildt
            (ISBN: 978-0071809252)
        \end{enumerate}

        \subsection{Supplemental Reading}

            \begin{enumerate}
                \item Design Patterns: Elements of Reusable Object-Oriented
                Software by Erich Gamma, Richard Helm, Ralph Johnson, John
                Vlissides (AUCA Library Call Number: QA 76.64 D47 1995, ISBN:
                978-0201633610)
                \item Refactoring: Improving the Design of Existing Code by
                Martin Fowler, Kent Beck, John Brant, William Opdyke, Don
                Roberts (AUCA Library Call Number: QA76.76.R42 F695 1999, ISBN:
                978-0201485677)
            \end{enumerate}

    \section{Grading}

        \begin{itemize}
            \item Practice tasks (30\%)
            \item Course project (40\%)
            \item Final examination (30\%)
        \end{itemize}

        \begin{itemize} \itemsep-10pt \parskip0pt \parsep0pt
            \item[--] 90\%--100\%: A\\
            \item[--] 80\%--89\%: A-\\
            \item[--] 70\%--79\%: B+\\
            \item[--] 65\%--69\%: B\\
            \item[--] 60\%--64\%: B-\\
            \item[--] 56\%--59\%: C+\\
            \item[--] 53\%--55\%: C\\
            \item[--] 50\%--52\%: C-\\
            \item[--] 46\%--49\%: D+\\
            \item[--] 43\%--45\%: D\\
            \item[--] 40\%--42\%: D-\\
            \item[--] Less than 39\%: F
        \end{itemize}

    \section{Rules}

        Students are required to follow the rules of conduct of the Software
        Engineering Department and American University of Central Asia.

        Team work is NOT encouraged. Equal blocks of code or similar structural
        pieces in separate works will be considered as academic dishonesty and
        all parties will get zero for the task.

\end{document}

